Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Renamed the data object

```{r echo=FALSE}
intervention_categories_fmd <- compact_data %>% 
  filter(disease == 'fmd') %>% 
  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
  count(is_vax_effective, sort = TRUE) %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  adorn_totals(where = 'col')

>>>>

```{r echo=FALSE}
intervention_categories_fmd <- data_fmd_only %>% 
  group_by(intervention_type, vax_modelled_with_non_vax) %>% 
  count(is_vax_effective, sort = TRUE) %>% 
  filter(vax_modelled_with_non_vax == 'yes') %>% 
  pivot_wider(names_from = is_vax_effective, values_from = n) %>% 
  adorn_totals(where = 'col')
